|

### 2023-02-04 paper.Rmd
Sat Feb  4 19:00:06 CET 2023: update-remote.sh

The objective of the airfoil problem is to find a function that accurately predicts the output variable $y$ by taking in a subset of the input variables $x1,x2,x3,x4,x5$. The function set used by all DAE-GP variations for symbolic regression is summarized in \@ref(tab:airfoil-fullRun-2hl-maxIndSize-params), the terminal set consists of the the input variables $x1,x2,x3,x4,x5$ and the ephemeral integer constants listed in \@ref(tab:airfoil-fullRun-2hl-maxIndSize-params)[@dae-gp_2022_symreg].

@@

```{r full-run-realWorldSymReg-problems, echo=FALSE, message=FALSE, warning=FALSE}
fig.pos="H"
knitr::kable(
  read.csv("./tables/full_run_realWorldSymReg_problems.csv"),
  caption="Real World Symbolic Regression Benchmark Problems",
  format = "markdown"
)%>% row_spec(0,bold=TRUE ) %>% kableExtra::kable_styling(latex_options = "hold_position")
```

Table X summarizes the median best fitness achieved after running each algorithm for 10 runs using a population size of 500 individuals for 30 generations.^[P-Values are marked with asterisk (1,2,3) for ($\alpha$)-levels of $0.1$, $0.05$ and $0.01$]. The median best fitness over all 30 generations are visualized in figure X.

@@

# Create the data frame from csv
df <- read.csv(
  "/Users/rmn/github/master_thesis/data/summary_table_final_fit_mean.csv",
  # "/Users/rmn/github/master_thesis/data/summary_table_final_fit_median.csv",  -> Use this path to summarize by median
  sep=",",
  colClasses = c("character", "numeric", "character", "numeric", "numeric", "character", "character")
)

@@

knitr::kable(
 df_bold,
 format = "markdown",
 col.names = col_names,
 align = "c",
 caption = "Median Best Fitness - Symbolic Regression"
) %>% row_spec(0,bold=TRUE ) %>% kableExtra::kable_styling(latex_options = "hold_position")

@@

![Median Best Fitness - Symbolic Regression](~/masterThesis/master_thesis/img/symbolicRegressionSummarized/median_fitness_byGens.png){height=80%}

## Solution Size in Symbolic Regression

Next I studied the size of solutions based on using a pre-training strategy. Figure X shows the median size of the best solutions aggregated of all benchmark problems for symbolic regression

![Median Solution Size - Symbolic Regression](~/masterThesis/master_thesis/img/symbolicRegressionSummarized/median_bestSol_size_byGens.png){height=80%}

Table X summarizes the results of the statistical tests.

@@

knitr::kable(
 df_bold,
 format = "markdown",
 col.names = col_names,
 align = "l",
 caption = "Median Solution Size - Symbolic Regression"
) %>% row_spec(0,bold=FALSE) %>% kableExtra::kable_styling(latex_options = "hold_position", font_size = 7)

@@

knitr::kable(
 df_bold,
 format = "markdown",
 col.names = col_names,
 align = "c",
 caption = "Median Population Diversity over Generations - Symbolic Regression"
) %>% 
  kable_styling(latex_options = "scale_down", font_size = 7)

>>>>

The objective of the airfoil problem is to find a function that accurately predicts the output variable $y$ by taking in a subset of the input variables $x1,x2,x3,x4,x5$. The function set used by all DAE-GP variations for symbolic regression is summarized in \@ref(tab:airfoil-fullRun-2hl-maxIndSize-params), the terminal set consists of the the input variables $x1,x2,x3,x4,x5$ and the ephemeral integer constants listed in table \@ref(tab:airfoil-fullRun-2hl-maxIndSize-params)[@dae-gp_2022_symreg].

@@

```{r full-run-realWorldSymReg-problems, echo=FALSE, message=FALSE, warning=FALSE}
fig.pos="H"
knitr::kable(
  read.csv("./tables/full_run_realWorldSymReg_problems.csv"),
  caption="Real World Symbolic Regression Benchmark Problems",
  format = "markdown"
)%>% row_spec(0,bold=TRUE ) %>% kableExtra::kable_styling(latex_options = "hold_position")
```
To test for statistical differences between the distributions of results achieved by either pre-trained or regular DAE-GP, I selected the  
nonparametric Mann-Whitney-U Test ([@mwu1], [@mwu2]) to test if the distribution .... Additionaly the effect strength of pre-training is computed by using Cliffs Delta[@Cliff1993DominanceSO].

## Fitness

The results for the median best fitness over the evolutionary search are visualized in figure \@ref(fig:symReg-Fitness).

```{r symReg-Fitness, echo=FALSE, fig.cap="Fitness over 30 Generations - Summary - Real World Symbolic Regression", out.width="80%"}
knitr::include_graphics("~/masterThesis/master_thesis/img/symbolicRegressionSummarized/median_fitness_byGens.png")
```

Table \@ref(tab:full-run-realWorldSymReg-fitness) summarizes the results for the median best fitness achieved after 30 generations and shows the results of computing the statistical tests. Higher fitness values (lower RMSE) are printed bold and p-values are marked with asterisk (1,2,3) for $\alpha$ levels ($0.1$, $0.05$, $0.01$).

@@

# Create the data frame from csv
df <- read.csv(
  #"/Users/rmn/github/master_thesis/data/summary_table_final_fit_mean.csv",
  "/Users/rmn/github/master_thesis/data/summary_table_final_fit_median.csv",
  sep=",",
  colClasses = c("character", "numeric", "character", "numeric", "numeric", "character", "character")
)

@@

knitr::kable(
 df_bold,
 format = "markdown",
 col.names = col_names,
 align = "l",
 caption = "Median Best Fitness after 30 generations - Summary - Real World Symbolic Regression"
) %>% row_spec(0,bold=TRUE ) %>% kableExtra::kable_styling(latex_options = "hold_position")

@@

## Solution Size

Next I studied the size of solutions found during DAE-GP. Figure \@ref(fig:symReg-Size) shows the median size of the best solution per generation aggregated over all benchmark problems for symbolic regression.

```{r symReg-Size, echo=FALSE, fig.cap="Size of the best Solution over 30 Generations - Summary - Real World Symbolic Regression", out.width="80%"}
knitr::include_graphics("~/masterThesis/master_thesis/img/symbolicRegressionSummarized/median_bestSol_size_byGens.png")
```

Table \@ref(tab:full-run-realWorldSymReg-best-solution-size) shows the median size of the best solution after 30 generations and results for computing the statistical tests.

@@

knitr::kable(
 df_bold,
 format = "markdown",
 col.names = col_names,
 align = "l",
 caption = "Median Size of the best solution after 30 generations - Summary - Real World Symbolic Regression"
) %>% row_spec(0,bold=FALSE) %>% kableExtra::kable_styling(latex_options = "hold_position", font_size = 7)

@@

knitr::kable(
 df_bold,
 format = "markdown",
 col.names = col_names,
 align = "l",
 caption = "Median Population Diversity over Generations - Symbolic Regression"
) %>% 
  kable_styling(latex_options = "scale_down", font_size = 7)
